Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-18 submission5/core.tex
Introduced state elements earlier

Finally, we define high-level security properties---integrity, confidentiality,
and well-bracketed control flow---in terms of the security classes of state
elements. These take the form of predicates on states and contexts
that use variants,
assertions about future return states, and comparison of event traces to capture the
desired behavior without reference to internal implementation details.
We introduce these properties by example in \cref{sec:example} and
formally in \cref{sec:formal}. In the remainder
of this section we describe the underlying framework in more detail.

@@

Where the caller's confidentiality and integrity are concerned with protecting specific,
identifiable state---the caller's stack frame---their callee equivalents are concerned
with enforcing the expected interface between caller and callee. Communication between
the principals should occur only through the state elements that are designated for the
purpose: those labeled \(\public\) and \(\object\). \sna{Define state elements before this. Priority 3.}

>>>>

Finally, we define high-level security properties---integrity, confidentiality,
and well-bracketed control flow---in terms of the security classes of {\em state elements}
(memory addresses and registers). The properties are predicates use variants, assertions
about future return states, and comparison of event traces to capture
desired behavior without reference to internal implementation details.

We introduce these properties by example in \cref{sec:example} and
formally in \cref{sec:formal}. In the remainder
of this section we describe the underlying framework in more detail.

@@

Where the caller's confidentiality and integrity are concerned with protecting specific,
identifiable state---the caller's stack frame---their callee equivalents are concerned
with enforcing the expected interface between caller and callee. Communication between
the principals should occur only through the state elements that are designated for the
purpose: those labeled \(\public\) and \(\object\).
